%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge Daniel Zou} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:17039390901}{(703) 939-0901}
    $|$
    \faEnvelope \hspace{.5pt} \href{mailto:dlzou@berkeley.edu}{dlzou@berkeley.edu}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/dlzou}{dlzou}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/dlzou}{dlzou}
    $|$
    \faGlobe \hspace{.5pt} \href{https://dlzou.github.io}{dlzou.github.io}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {University of California, Berkeley}{Berkeley, CA}
      {B.Sc. Electrical Engineering and Computer Sciences, with Honors; \textbf{GPA: 3.94/4.00}}{Aug 2019 -- May 2023}
    
    \resumeSubheading
      {Academy of Science and Technology}{The Woodlands, TX}
      {High School Diploma; \textbf{Rank: 2/712}}{Aug 2015 -- May 2019}
    
  \resumeSubHeadingListEnd



%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Berkeley Sky Computing Lab}{Berkeley, CA}
      {Undergraduate Research Assistant}{Sep 2022 -- Present}
        \resumeItemListStart
            \resumeItem{Contributed to \href{https://github.com/alpa-projects/alpa}{Alpa}, a system for automatically parallelizing the training and serving of large-scale neural networks.}
            \resumeItem{Implemented swapping between GPU and main memories in the Alpa runtime to enable deployment of large models on clusters with limited GPU memory resources.}
            \resumeItem{Supervised by Lianmin Zheng and Professor Joesph Gonzalez.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Berkeley RISE Lab}{Berkeley, CA}
      {Undergraduate Research Assistant}{Mar 2021 -- Present}
        \resumeItemListStart
            \resumeItem{Contributed to \href{https://github.com/nums-project/nums}{NumS}, a high performance distributed numerical library for Python with a NumPy-like interface, with support for Ray and Dask backends.}
            \resumeItem{Studied and innovated on techniques like operator fusion and cost estimation to dynamically schedule sparse-aware tensor operations on multi-node systems.}
            \resumeItem{Implemented distributed algorithms such as quickselect for block-partitioned arrays, then analyzed the scaling properties of said algorithms through benchmarks on an EC2 cluster.}
            \resumeItem{Supervised by Melih Elibol, PhD and Professor Ion Stoica.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {NVIDIA Corporation}{Santa Clara, CA}
      {Autonomous Vehicles Software Infrastructure Intern}{May 2022 -- Aug 2022}
        \resumeItemListStart
            \resumeItem{Designed and built on-call automation and metrics collection tooling from the ground up, for use by NVIDIA's AV infrastructure organization.}
            \resumeItem{Architected a concurrent, event-driven service with WebSockets, producer-consumer queue, in-memory cache, SQL database, and a querying command interface.}
            \resumeItem{Worked with multiple stakeholder representatives to revise features and improve usability of the tooling during development and beta testing. Presented the product to 50+ engineers and managers, then engaged with discussions of expanding product scope to other organizations.}
            \resumeItem{Deployed for use by 300+ engineers and business partners, and growing.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

\section{Organizations}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Computer Science Undergraduate Association}{Berkeley, CA}
      {VP of Technology \& Root Staff}{Sep 2020 -- Aug 2022}
        \resumeItemListStart
            \resumeItem{Administered a GPU cluster, a web hosting server, and other free computing services used by 400+ members.}
            \resumeItem{Maintained a full stack web application written in Django.}
            \resumeItem{Configured a multi-instance Postfix mail server.}
            \resumeItem{Served as the leader of CSUA Root Staff for a semester upon election to VP of Technology. Acted as liaison with campus IT staff to resolve issues regarding networking services.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Computer Science Mentors}{Berkeley, CA}
      {Junior Mentor}{Jan 2021 -- May 2021}
        \resumeItemListStart
            \resumeItem{Taught CS 61C: Great Ideas in Computer Architecture, which covers C, RISC-V assembly, CPU logic design, memory hierarchy, and parallel programming.}
            \resumeItem{Mentored a group of student every week by giving short lectures and practice problem walk-throughs.}
        \resumeItemListEnd
    
    \resumeSubheading
      {FIRST Robotics Team 1477 (Texas Torque)}{The Woodlands, TX}
      {Lead Programmer}{Jun 2018 -- May 2019}
        \resumeItemListStart
            \resumeItem{Recruited a team of 6 programmers and oversaw the development of the robot control system.}
            \resumeItem{Designed new autonomous control framework that enables scheduling actions for multiple subsystems in parallel. Built a custom object tracking CV pipeline that runs on a coprocessor.}
            \resumeItem{Reached the quarterfinal of the 2019 FRC World Championship as a team.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- PUBLICATIONS ------------



%----------- PROJECTS -----------

\section{Selected Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{PintOS}}{}
          \resumeItemListStart
            \resumeItem{An instructional OS written in C and x86. Completed in CS 162: Operation Systems and Systems Programming over the course of a semester.}
            \resumeItem{Implemented basic user processes, kernel threads, concurrency primitives, and concurrent filesystem.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{NP-Hard Graph Problem Solver} $|$ \emph{\href{https://github.com/dlzou/cs170-project}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{An open-ended project to find optimal solutions for a set of inputs to a given NP-hard graph problem. Completed in CS 170: Efficient Algorithms and Intractable Problems.}
            \resumeItem{Designed a greedy algorithm as a baseline and a simulated annealing algorithm to explore the space of potentially better solutions. Wrote scripts to to merge best solutions over multiple runs.}
          \resumeItemListEnd
      
      \resumeProjectHeading
      {\textbf{NumC: Toy Reimplementation of Core NumPy Functionality}}{}
        \resumeItemListStart
          \resumeItem{Completed in CS 61C: Great Ideas in Computer Architecture.}
          \resumeItem{Lightweight numerical library for Python, with underlying data structures written in C for performance.}
          \resumeItem{Support efficient matrix slicing and common operations like add, abs, matmul, matpow. Optimized matmul with threading, loop tiling, and SIMD intrinsics. Optimized matpow with dynamic programming.}
        \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Deep NLP Chatbot} $|$ \emph{\href{https://dlzou.github.io/2020/08/30/deep-nlp-chatbot-using-a-seq2seq-model/}{\color{blue}Blog}}}{}
          \resumeItemListStart
            \resumeItem{Self-studied RNNs and its variants, as well as the TensorFlow ML framework.}
            \resumeItem{Implemented an attention-based seq2seq model that uses a beam search decoder for evaluation.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{National Merit Finalist: }{Selected among high school seniors scoring in the top 0.5\% of the PSAT.} \\ \vspace{3pt}
        
        \textbf{American Invitational Mathematics Exam Qualifier: }{Scored in the top 5\% of students taking AMC 10 \& 12.}
    }}
  \resumeSubHeadingListEnd



%----------- SKILLS -----------
 
\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming: }{Python, C, Go, Java, OCaml, Lua, SQL, RISC-V, x86} \\ \vspace{3pt}
        
        \textbf{Libraries: }{SciPy, PyTorch, JAX, Ray, Spark, Django} \\ \vspace{3pt}
        
        \textbf{Technologies: }{Linux, Git, Jira, Docker, AWS EC2} \\ \vspace{3pt}

        \textbf{Other: }{native English and Mandarin Chinese, technical and blog writing}
    }}
  \resumeSubHeadingListEnd



%----------- SELECTED COURSEWORK -----------

\section{Selected Coursework}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{CS 61C: }{Gread Ideas in Computer Architecture} \\ \vspace{3pt}

        \textbf{CS 161: }{Computer Security} \\ \vspace{3pt}

        \textbf{CS 162: }{Operating Systems and Systems Programming} \\ \vspace{3pt}
        
        \textbf{CS 164: }{Programming Languages and Compilers} \\ \vspace{3pt}
        
        \textbf{CS 170: }{Efficient Algorithms and Intractable Problems} \\ \vspace{3pt}
        
        \textbf{CS 182: }{Deep Neural Networks} \\ \vspace{3pt}
        
        \textbf{CS 186: }{Introduction to Database Systems} \\ \vspace{3pt}
        
        \textbf{CS 189: }{Introduction to Maching Learning} \\ \vspace{3pt}
        
        \textbf{ENGIN 185: }{The Art of STEM Communication} \\ \vspace{3pt}
        
        Please refer to my transcript for a full record of my technical and non-technical coursework.
    }}
  \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
    
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
